Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-02 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
Some work towards a draft of RSE funding section

\todo{add POC here}

This is where the bit I need to write will go.

@@

Don Middleton
Josh Greenburg: SLOAN
James Hetherington: University College London j.hetherington@ucl.ac.uk
Lindsay Powers: The HDF Group, lpowers@hdfgroup.org
Mark Miller
Dan Sellars: CANARIE

\begin{itemize}
\item name -- affiliation
\item name2 -- affiliation2
\end{itemize}

>>>>

James Hetherington\footnote{email: \href{mailto:j.hetherington@ucl.ac.uk}{j.hetherington@ucl.ac.uk}}
will serve as the point of contact for this working group, and be responsible for ensuring timely progress of the planned actions.

@@

Don Middleton -- National Center for Atmospheric Research
Joshua Greenberg -- Alfred P. Sloan Foundation
James Hetherington -- University College London
Lindsay Powers -- The HDF Group
Mark Miller
Dan Sellars: CANARIE

\begin{itemize}
\item Don Middleton -- National Center for Atmospheric Research
\item Josh Greenburg -- affiliation2
\end{itemize}

### 2015-11-02 WSSSPE3/report/wg_main_funding_spec_expert.tex
Some work towards a draft of RSE funding section

\subsubsection{Why it is important}
\todo{short text here}

\subsubsection{Fit with related activities}
\todo{short text here - can include links/cites}

>>>>

\subsubsection{Why it is important}

Research Software Engineers -- those who contribute to science and scholarship
through computer programming -- are an important part of the team
needed to deliver 21st century research. However, existing academic structures
and systems of funding do not effectively fund and sustain these skills.
The resulting high levels of turnover, and inappropriate incentivisation,
are a significant contributing factor to low levels of reliability and
readability observed in scientific software.

\subsubsection{Fit with related activities}

One solution to this problem would be a successful solution to the problems of
obtaining academic credit for programming work. If this were solved, traditional
academic funding models and career tracks would properly sustain this
contribution to research.
